\huge Tor's Usability for Censorship Circumvention

### 2016-04-19 pets2017-paper/pets2017-paper.tex
evaluation and setup sections

\section{Goals/Evaluation Criteria}
\label{sec:goals}
In the course of our experiments we evaluated two versions
of the Tor Launcher interface.
The first, which we have labeled ``OLD'' in figures and tables,
is the current version being distributed with Tor Browser.
The second, ``NEW'', is the prototype we revised and redesigned
in order to provide better usability.
We evaluate the old and new interfaces
through the empirical evaluation and heuristic evaluation criteria below.

@@

\begin{enumerate}
    \item  {\bfseries Visibility of system status:} Provide feedback on what the system is doing. 
    \item  {\bfseries Error management:} Expressing errors in plain language and offering a solution. 
    \item  {\bfseries Understandable language:} Explaining the task, rather than technical concepts. 
    \item  {\bfseries Simple design:} Showing options on an as-needed basis. 
\end{enumerate}

Our empirical evaluation criteria for the Tor Browser configuration
interface are from common metrics that measure ease of use with a special 
consideration for high-risk users: \\

\begin{enumerate}
    \item {\bfseries Task completion rate:} Almost all can successfully connect to Tor.
    \item {\bfseries  Time to completion:} Measured between program startup and successful connection to Tor.
    \item {\bfseries Safety for high-risk users:} It should be possible to configure Tor without leaking the fact that the user is using Tor. 
\end{enumerate}

\subsection{Censorship Environments}
\label{sec:environments}
In each experiment, we simulated three censorship environments,
which we labeled ``E1,'' ``E2,'' and ``E3''
in order of increasing severity.
We designed the environments to be representative
of what, in our estimation, are important real-world
cases of censorship, but they are not intended to imitate
any particular country's censorship exactly.

@@

Table~\ref{tab:environments} summarizes what is blocked
in each environment.
We used features of the Windows operating system to implement
the above environments.
To simulate website blocking, we added entries to the hosts file,
mapping domain names to the address 127.0.0.1.
For IP address blocking, we used Windows Firewall rules.

@@

All our experiments use (modified versions of)
Tor Browser~5.0.3, which was the most recent stable release at the time we began~\cite{torbrowser-503}.
Though there were new releases during the course of the experiments,
we stuck with 5.0.3 so as not to introduce potential confounding factors.

>>>>

\section{Evaluation Criteria and Goals}
\label{sec:goals}
The series of user studies evaluated two versions of the Tor Launcher interface.
The first, which we have labeled ``OLD'' in figures and tables,
is the current version being distributed with Tor Browser.
The second, ``NEW'', is the prototype we revised and redesigned
in order to provide better usability. Below are the empirical and 
heuristic evaluation criteria we use to assess the interfaces.

Our empirical evaluation criteria for the Tor Browser configuration
interface are from common metrics that measure ease of use: \\

\begin{enumerate}
    \item {\bfseries Task completion rate:} What percentage of users can successfully connect to Tor in a given condition.
    \item {\bfseries  Time to completion:} How long it takes between program startup and a successful connection to Tor.
    \item {\bfseries Active configuration time:} How much time a user spends actively configuring network components to connect to Tor. 
\end{enumerate}

@@

\begin{enumerate}
    \item  {\bfseries Visibility of system status:} There is feedback on system state is and what the system is doing. 
    \item  {\bfseries Error management:}  Errors are in plain language and offers a solution. 
    \item  {\bfseries Understandable language:} Users are able to understand the text and concepts mentioned in the interface. 
\end{enumerate}

An ideal interface would guide users though the configuration process while communicating system state and managing errors along the way. Users would be able to connect to the Tor network in a couple of minutes.

\section{Experimental Setup}
\label{sec:environments}
For our experiments, we use (modified versions of) Tor Browser~5.0.3, 
the most recent stable release at the time~\cite{torbrowser-503}.
Though there were new releases during the experiments,
we tested the same version across all participants to not introduce
confounding factors.

For both user studies, we simulated three censorship environments,
which we refer to as ``E1,'' ``E2,'' and ``E3,'' in order of increasing severity.
We designed the environments to be representative
of what, in our estimation, are important real-world
cases of censorship. They are not intended to imitate
any particular country's censorship environment.

@@

Table~\ref{tab:environments} summarizes our simulated censorship
environments. We used features of the Windows operating system 
to implement the above blocking behaviors.
To simulate website blocking, we added entries to the hosts file,
mapping domain names to the address 127.0.0.1.
For IP address blocking, we used Windows Firewall rules.

@@
